\documentclass{moumita_cv}

\setname{Moumita}{Chakraborty}
\setaddress{Dinajpur/Bangladesh}
\setmobile{+8801701080864}
\setmail{moumitaswarno.ruet15@gmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/moumita-chakraborty-771331145/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/Moumita110} %you can play with color of the template (red is also nice..)
\setthemecolor{cyan} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Career Objective}{%
\ To obtain a fresher position as a software engineer in a fast-paced organization where I’ll get chance to use my technical skills and academic knowledge for the development of the project, where a dynamic learning environment is ensured. I would like to serve with full sincerity, dignity, and honesty to contribute to the development of the organization and excel my personal and technical growth. 

  \ %replace this part with actual text
}
%
%Education
\section{Education} 
    \datedexperience{Rajshahi University of Engineering \& Technology}{jan. 2016-Mar. 2021} 
    \explanation{{B.S in Computer Engineering} {CGPA: 3.02/4.00}}
     }
    \datedexperience{Dinajpur Govt. Women's College}{Jun. 2013- Jan. 2015} 
    \explanation{{Higher Secondary Certificate} {GPA: 5.00/5.00}}
     }
     \datedexperience{Dinajpur Govt. Girls' High School}{Jan. 2005- Dec. 2012} 
     \explanation{{Secondary School Certificate} {GPA: 5.00/5.00}} 
     }
%
% Experience
\section{Project Experience}
    %
    \datedexperience{Hand sign detection using CNN}{} 
    \explanation{A computer vision model to classify hand signs images using Raspberry Pi and deep convolutional neural network.} 
      \explanation{\underline{\href{https://github.com/Moumita110/6th-semester-project}{https://github.com/Moumita110/6th-semester-project}}}
    %
    \datedexperience{Fuel efficiency prediction}{} 
    \explanation{Deep learning, Convolutional Neural Network} 
    \explanation{\underline{\href{https://github.com/Moumita110/Fuel-efficiency-prediction}{https://github.com/Moumita110/Fuel-efficiency-prediction}}}
    %
     \datedexperience{Detecting COVID-19 from Chest X-ray images}{} 
    \explanation{Deep learning, Convolutional Neural Network}      \explanation{\underline{\href{https://github.com/Moumita110/covid19_prediction}{https://github.com/Moumita110/covid19_prediction}}}
    %
    \datedexperience{Game project: Memory\_Game}{} 
    \explanation{Simple javascript game project using HTML, CSS, javascript } 
    \explanation{\underline{\href{https://github.com/Moumita110/Memory_game}{https://github.com/Moumita110/Memory_game}}}
     \datedexperience{Game project: Connect\_Four}{} 
    \explanation{Simple javascript game project using HTML, CSS, javascript }
    \explanation{\underline{\href{https://github.com/Moumita110/Connect_four}{https://github.com/Moumita110/Connect_four}}}
     }
    %  
     }
    %
     }
%
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}
    {C \cpshalf C++ \cpshalf Python }}
    %
    \newcommand{\skilltwo}{\createskill{Web based Language}{Javascript\cpshalf PHP\cpshalf HTML5 \cpshalf CSS }}
    %
    \newcommand{\skillthree}{\createskill{Database Language}{MySql\cpshalf Oracle}}
    %
    \newcommand{\skillfour}{\createskill{Others}{Problem Solving \cpshalf Matlab \cpshalf Adobe Illustrator\cpshalf Adobe photoshop }}
    %
    \newcommand{\skillfive}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Bangla \ \ \textbf{\emph{Fluent:}} \ \ English \ \ \ \ }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive}

\section{Research}
 \datedexperience{Classification of Pneumonia using convolutional neural network from chest x-ray images. }{} \explanation{Deep Learning, Python, Tensorflow, Keras } 
 \explanation{Tools used: Tensorflow, keras, matplotlib}
 \explanation{\underline{\href{https://github.com/Moumita110/Pneumonia-classification}{https://github.com/Moumita110/Pneumonia-classification}}} \\
 \\
 \\
    \explanation{\textbf{Fields of research interest:}}
     \newcommand{\extraone}{Data Science\par
    }
    \newcommand{\extratwo}{Machine Learning\par %replace this part with actual text
    }
    \newcommand{\extrathree}{Deep Learning\par %replace this part with actual text
    }
    \newcommand{\extrafour}{Image Processing\par %replace this part with actual text
    }
    %
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree, \extrafour}
    %
    \createbullets{\listofextras}
    % 
 %
\section{Problem Solving Experience}
 %
 \datedexperience{Hackerrank}{} 
    \explanation{Solved 150+ problems} 
    \explanation{Profile Link: \underline{\href{https://www.hackerrank.com/swarno?hr_r=1}{https://www.hackerrank.com/swarno?hr_r=1}} }
   
    % 
 %
\section{Extra Curricular Involvement}
\datedexperience{Former active member of Astronomy \& Science Society of RUET (ASSR) }{2017-2019} \explanation{Public Speaking, Leadership \& Team work 
    }
    
 %
\section{Reference}
 \explanation{\textbf{ Dr. Md Nazrul Islam Mondal}}
 \explanation{ Professor}
 \explanation{ Dept of Computer science \& Engineering}
 \explanation { Rajshahi University of Engineering \& Technology}
 \explanation{ Phone:   +880-1720662278 , +880-1912744327 }
 \explanation{ Email:  {nimbd109@gmail.com}}
%
 %


%Footnote

\end{document}
